Smoothing seismicity techniques applied to seismic source characterization and probabilistic seismic hazard analysis in Brazil

### 2015-02-13 manuscript.tex
some figure changes, add histogram (counting) model uniform catalogs...

The seismicity \gls{kde} or the smoothed seismicity grid allow to define a grid of seismic point sources. The seismic rate (\emph{a}-value) associated to each source is defined by the smoothed seismicity methods, but the other parameters, like \emph{b}-values, minimum and maximum magnitudes, rupture and depth distributions, must be assigned in other ways.

@@

@@

\begin{table}[H]
	\caption{BSB 2014.11 $M_W$ proxies \emph{ad-hoc} guidelines.}
	\begin{tabular}{l l l}
		\hline
		\textbf{magnitude source} & \textbf{rule} & \textbf{uncertainty}\\
		\hline
		% mb or equival & $$ M_W = 1.21m - 0.76 $$  & 0.3 \\
		% 		% magnitude from $A_f$  & $$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 8.4\times10^{-4}A_f^{1/2}& 0.4 \\
		$mb$ or $mR$
		&$ M_W(m) = 1.121 m - 0.76 $
		& 0.3 \\
		Area felt $A_f$
		&$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 0.00084\sqrt{A_f}$& 0.4 \\
		Maximum intensity $I_0$
		& $mb(I_0) = 1.21 + 0.45 I_0$ then $M_W(m)$
		& 0.6 \\
		$mb$ and $A_f$
		& $M_W(m, A_f) = 0.7 M_W(m) + 0.3 M_W(A_f)$
		& 0.33 \\
		\hline
	\end{tabular}
	\label{tab:guidelines}
\end{table}

>>>>

The \gls{kde} (or smoothed) seismicity grid allow to define a grid of seismic point sources. The seismic rate (\emph{a}-value) associated to each source is defined by the smoothed seismicity methods, but the other parameters, like \emph{b}-values, minimum and maximum magnitudes, rupture and depth distributions, must be assigned in other ways.

@@

\begin{figure}
	\begin{center}
	\begin{table}[H]
		\begin{tabular}{ p{0.25\textwidth}
						 p{0.25\textwidth}
						 p{0.25\textwidth}
						 p{0.25\textwidth} }
		\footnotesize(a) &
		\footnotesize(b) &
		\footnotesize(c) &
		\footnotesize(d)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_assump_25}  &
		\includegraphics[height=4cm]{z_img_f_assump_50_25} &
		\includegraphics[height=4cm]{z_img_f_assump_150_025} &
		\includegraphics[height=4cm]{z_img_woo_assump_25} 
		\\
		\footnotesize(e) &
		\footnotesize(f) &
		\footnotesize(g) &
		\footnotesize(h)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_stepp_25}  &
		\includegraphics[height=4cm]{z_img_f_stepp_50_025} &
		\includegraphics[height=4cm]{z_img_f_stepp_150_025} &
		\includegraphics[height=4cm]{z_img_woo_stepp_25} 
		\\
		\footnotesize(i) &
		\footnotesize(j) &
		\footnotesize(l) &
		\footnotesize(m)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_assump_50}  &
		\includegraphics[height=4cm]{z_img_f_assump_50_50} &
		\includegraphics[height=4cm]{z_img_f_assump_150_050} &
		\includegraphics[height=4cm]{z_img_woo_assump_50} 
		\\
		\footnotesize(n) &
		\footnotesize(o) &
		\footnotesize(p) &
		\footnotesize(q)
		\\
		\includegraphics[height=4cm]{z_img_2dhist_stepp_50}  &
		\includegraphics[height=4cm]{z_img_f_stepp_50_050} &
		\includegraphics[height=4cm]{z_img_f_stepp_150_050} &
		\includegraphics[height=4cm]{z_img_woo_stepp_50}

		\end{tabular}
	\end{table}
	\caption{Smoothed rates comparission: (a) shows \citet{frankel_1995} method smoothed rate results, (b) and (c) represent rates smoothed by \citet{woo_1996} and \citet{helmstetter_2012} methods respectly.}
	\label{fig_rates2}
	\end{center}
\end{figure}

@@

\begin{table}[H]
	\caption{BSB 2014.11 $M_W$ proxies \emph{ad-hoc} guidelines.}
	\begin{tabular}{l l l}
		\hline
		\textbf{magnitude source} & \textbf{rule} & \textbf{uncertainty}\\
		\hline
		% mb or equival & $$ M_W = 1.21m - 0.76 $$  & 0.3 \\
		% 		% magnitude from $A_f$  & $$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 8.4\times10^{-4}A_f^{1/2}& 0.4 \\
		$mb$ or $mR$
		&$ M_W(m) = 1.121 m - 0.76 $
		& 0.3 \\
		Felt area$A_f$
		&$ M_W(A_f) = 0.81 $$    + 0.639\log(A_f) + 0.00084\sqrt{A_f}$& 0.4 \\
		Maximum intensity $I_0$
		& $mb(I_0) = 1.21 + 0.45 I_0$ then $M_W(m)$
		& 0.6 \\
		$mb$ and $A_f$
		& $M_W(m, A_f) = 0.7 M_W(m) + 0.3 M_W(A_f)$
		& 0.33 \\
		\hline
	\end{tabular}
	\label{tab:guidelines}
\end{table}
